### 2016-03-06 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation. However, in many Computer Vision problems,
state-of-the-art algorithms are still inherently sequential. Take a
Fusion-Move algorithm (FM)~\cite{viktor,second_order_stereo,else} for
example. FM was first introduced by Lempitsky et al. in solving an
optical flow problem. FM allows one to customize domain-specific
proposal generation schemes to achieve efficient convergence. FM has
been a very successful optimization framework in solving many
challenging problems in Computer Vision such as optical flow, stereo,
image denoising, image inpainting, or image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
main limitation of FM is its running time, where Computer Vision
researchers and engineers generally consider FM to be a slow algorithm
that can solve challenging problems by fusing hundreds or sometimes
thousands of proposals sequentially.
%
The running time becomes particularly an issue for large

image denoising for high resolution images (24mb), high resolution
map-tile image stitching (satellite), voxel CRF~\cite{pollefeys}

\yasu{Are there any concrete examples where MRF is used to solve a very
large problem where parallel fusion is really helpful. Like denoising
high resolution 24M pixel images. Stitching a high resolution map tiles
(satellite image tiles) via image stitching.}

>>>>

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation.

As image sensor technologies improve, Computer Vision need to deal with
large-scale inference problems more than ever.

However, in many Computer Vision problems,
state-of-the-art algorithms are still inherently sequential. Take a
Fusion-Move algorithm (FM)~\cite{viktor,second_order_stereo,else} for
example. FM was first introduced by Lempitsky et al. in solving an
optical flow problem. FM allows one to customize domain-specific
proposal generation schemes, a main advantage over general solvers such
as message passing algorithms. FM has been a very successful
optimization framework in solving many challenging problems in Computer
Vision such as optical flow, stereo, image denoising, image inpainting,
or image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
main limitation of FM is its running time, where Computer Vision
researchers and engineers generally consider FM to be a slow algorithm
that can solve challenging problems, as hundreds or sometimes thousands
of proposals need to be fused sequentially.
%
The running time becomes particularly an issue for large data, for
instnance, image denoising of professional-grade high resolution (50
Mpixels) images, image stitching for the

generating a high resolution map-tiles (e.g., satellite) by stitching
hundreds of photographs

generation of high resolution
map-tiles (e.g., satellite), or volumetric joint reconstruction and
segmentation potentiallly a trillion ($=1024^3$) voxels~\cite{Joint 3D
Scene Reconstruction and Class Segmentation}.
\yasu{Are there any concrete examples where MRF is used to solve a very
large problem where parallel fusion is really helpful. Like denoising
high resolution 24M pixel images. Stitching a high resolution map tiles
(satellite image tiles) via image stitching.}
